\begin{bibsection}
	\item Wood, J.G., and J.K.~Hedrick. Partition Learning for Multiagent Planning. \emph{Journal of Robotics}. Volume 2012, Article ID 590479. 2012. 
	
    \item Wood, J.G. Time Evolving Space Partitioning for Search and Tracking of an
		Unknown Number of Targets by a Team of Heterogeneous Autonomous Agents. Dissertation, 				University of California, Berkeley. 2011.
	
	\item Wood, J.G., and J.K.~Hedrick. Multi-agent Path Planning for an
    	Unknown Number of Targets over Dynamic Space Partitions.
        In: \emph{Proceedings of the 50th IEEE Conference on Decision
        and Control and European Control Conference (CDC-ECC~2011)},
        December 12--15, 2011.

    \item Wood, J.G., and J.K.~Hedrick. Space Partitioning and Classification
    	for Multi-target Search and Tracking by Heterogeneous Unmanned Aerial
    	System Teams. In: \emph{Proceedings of the 2011 AIAA Infotech@Aerospace
    	Conference}, March 28, 2011.
	
	\item Wood, J.G., B.~Kehoe, and J.K.~Hedrick. Target Estimate PDF-based
    	Optimal Path Planning Algorithm with Application to UAV Systems. In:
    	\emph{Proceedings of the 2010 ASME Dynamic Systems and Control Conference},
        September 13, 2010.

    \item Wood, J.G. Reliable Wireless Sensor Network for Data Acquisition. Thesis,
		University of California, Berkeley. 2008.
	
	\item Wood, J.G., and S.~Mascaro. Human Finger Muscle-Tendon System for Robotics.
		In: \emph{Utah Undergraduate Research Journal}, 6, pp. 75, 112. 2006.
	
	\item Garvey, J., B.~Kehoe, B.~Basso, M.~Godwin, J.~Wood, J.~Love, S.-Y.~Liu,
    	Z.~Kim, S.~Jackson, Y.~Fallah, T.~Fu, R.~Sengupta, and J.K.~Hedrick. An
    	Autonomous Unmanned Aerial Vehicle System for Sensing and Tracking. In:
    	\emph{Proceedings of the 2011 AIAA Infotech@Aerospace Conference},
        March 28, 2011.
    	
	\item Sengupta, R., J.~Connors, B.~Kehoe, Z.~Kim, T.~Kuhn, and J.~Wood.
        Final Report -- Autonomous Search and Rescue with ScanEagle. Prepared for
        Evergreen Unmanned Systems and Shell International Exploration and
        Production Inc., September, 2010.
\end{bibsection}