\textbf{Hadal}\\
Oakland, California USA
\begin{outerlist}
\item[] \textit{Research \& Software Development}%
        \hfill \textbf{Feb 2014 to current}
\begin{innerlist}
\item Autonomous deep sea vehicle.
\item Mostly working on perception tasks to detect seafloor and moving obstacles using sonar-based range images. Also working on motion planning to safely follow seafloor and avoid obstacles.
\item Implemented in C++, some prototyping in Python.
\end{innerlist}
\end{outerlist}

\halfblankline

\textbf{Automa Aurora}\\
Berkeley, California USA
\begin{outerlist}
\item[] \textit{Software Development}%
        \hfill \textbf{Jun 2012 to Oct 2013}
\begin{innerlist}
\item Vehicle routing cloud service.
\item Built entire software system that included core distributed optimization algorithm, network communication, mobile app development.
\item Implemented in Java, Objective-C, Python.
\end{innerlist}
\end{outerlist}

\halfblankline

\href{http://www.utrc.utc.com/}{\textbf{United Technologies Research Center at Berkeley}}
\begin{outerlist}
\item[] \textit{Research and Development}%
        \hfill \textbf{Sep 2011 to Apr 2012}
\begin{innerlist}
\item Autonomous helicopter.
\item Implemented particle filter and object detection likelihood functions for target prediction and tracking.
\item Implemented in C++.
\end{innerlist}
\end{outerlist}

\halfblankline

\href{http://c3uv.berkeley.edu/}{\textbf{Center for Collaborative Control of Unmanned Vehicles}}\\
\href{http://vehicle.me.berkeley.edu/}{\textbf{Vehicle Dynamics Lab}}\\
\textbf{University of California$-$Berkeley}
\begin{outerlist}
\item[] \textit{Research \& Development}%
        \hfill \textbf{Aug 2007 to Sep 2011}
\begin{innerlist}
\item Autonomous aircraft pedestrian tracking.
\item Implemented perception, target track prediction, and motion planning to detect and follow pedestrians on the ground.
\item Implemented in C++.
\end{innerlist}
\end{outerlist}

\halfblankline

\href{http://www.lbl.gov/}{\textbf{Lawrence-Berkeley National Lab}}\\
\textbf{University of California$-$Berkeley}
\begin{outerlist}
\item[] \textit{Research \& Development}%
        \hfill \textbf{May 2006 to Aug 2007}
\begin{innerlist}
\item Implemented software for wireless sensor network high-frequency low-power sampling and communication.
\item Implemented in C, Java.
\end{innerlist}
\end{outerlist}

%\halfblankline
%
%\href{http://www.mech.utah.edu/}{\textbf{Mechanical Engineering Department}}\\
%\textbf{University of Utah}\\
%Salt Lake City, Utah USA
%\begin{outerlist}
%\item[] \textit{Undergraduate Researcher}%
%        \hfill \textbf{Nov 2004 to May 2006}
%\begin{innerlist}
%\item Various projects: developed bio-inspired robot finger actuator, automated image processing, assisted in wind tunnel experiments, implemented software (Java, Matlab).
%\end{innerlist}
% FULL DETAIL %%
%\item[] \textit{Undergraduate Research Traineeship}%
%        \hfill \textbf{May 2005 to May 2006}
%\begin{innerlist}
%\item Research and develop anthropomorphic robotic finger actuator system.
%\item Derive system of equations to model finger tendon displacement joint kinematics.
%\item Develop visualization software in Java.
%\end{innerlist}
%
%%\halfblankline
%
%\item[] \textit{Undergraduate Researcher}%
%		\hfill \textbf{September 2005 to May 2006}\\
%		Advanced Fluid Dynamics Lab
%\begin{innerlist}
%\item Develop oil-film interferometry analysis software with \Matlab.
%\item Develop graphical software for removing noise and analyzing digital images.
%\end{innerlist}
%
%%\halfblankline
%
%\item[] \textit{Undergraduate Researcher}%
%		\hfill \textbf{January 2005 to August 2005}\\
%		Physical Fluid Dynamics Lab
%\begin{innerlist}
%\item Develop graphical data acquisition control software for fluid flow visualization experiments.
%\end{innerlist}
%
%%\halfblankline
%
%\item[] \textit{Undergraduate Research Assistantship}%
%		\hfill \textbf{November 2004 to August 2005}\\
%		Thermal-fluids Lab
%\begin{innerlist}
%\item Assist in experiments with transonic wind tunnel to determine aerodynamic losses due to effects of surface roughness with varying Mach number and turbulence. 
%\end{innerlist}
%\end{outerlist}